---
title: "Puget Sound Downscaling"
output: html_notebook
---

Loading files
```{r warning=TRUE}
source("libraries.R")
source("map_Puget_Sound.R")
source("get_nc.R")
source("get_historical_nc.R")
source("combine_ncfiles.R")
source("regrid_ncfiles.R")
source("climatology_nc.R")
source("calc_anomaly.R")
source("interpolate_nc.R")
source("overlay_anomaly.R")
source("plot_interpolated_SST_anomaly.R")
#commented because it is a script and not a function
#source("plot_nc.R")
```

Creating Puget Sound Map
```{r}
make_map(shape.file = "~/Puget_Sound_Downscaling/Atlantis_shapefile/bgm_Puget_Sound_89b_0p0001_WGS84.shp", basin.shapefile = "~/Puget_Sound_Downscaling/repsbasin_shapefile/shapefile_4071.shp", file.name = "puget_sound_map.jpg", scale.factor = 1, arrow.position = "tr", min.long = -124.555, max.long = -121.9, min.lat = 46.9936, max.lat = 48.957)
```

Downloading initial files to test resolution
```{r}
model.list = c("HadGEM3-GC31-LL","EC-Earth3", "MRI-ESM2-0", "NorESM2-LM", "NorESM2-MM", "CMCC-CM2-SR5", "AWI-CM-1-1-MR")
lapply(model.list, get_nc)
system("az vm deallocate --name atlantisserver01 --no-wait --resource-group morzariacedogroup")

#get_nc(model.name = "AWI-CM-1-1-MR")

```

Downloading more files to test resolution
- These are higher resolution models that didn't run all as many ScenarioMIPs, so they were downloaded using ssp245
```{r}
model.list2 = c("GFDL-CM4", "GFDL-ESM2M", "CMCC-CM2-SR5")
lapply(model.list2, get_nc)
system("az vm deallocate --name atlantisserver01 --no-wait --resource-group morzariacedogroup")

```

Downloading even more files to test resolution
-GFDL and CMCC but with monthly data
```{r}
model.list3 = c("GFDL-CM4", "CMCC-CM2-SR5")
lapply(model.list3, get_nc)
system("az vm deallocate --name atlantisserver01 --no-wait --resource-group morzariacedogroup")
```

Plotting model resolutions
```{r}
setwd("~/Puget_Sound_Downscaling/plotting_models/")

source("plot_AWI-CM-1-1-MR.R")
source("plot_CNRM-CM6-1-HR.R")
source("plot_GDFL-CM4.R")

```


Download SST data for all scenarios
```{r}
model.list.download  <- c("GFDL-CM4", "CNRM-CM6-1-HR")
#model.list.download  <- c("CNRM-CM6-1-HR")

#sets working directory
setwd("~/Puget_Sound_Downscaling/data_files/")

#ScenarioMIP

data.cimp6.sc <- lapply(model.list.download, get_nc, model.var = "tos") %>% 
  bind_rows

#Historical data
#salinity is "sos"
data.cimp6.hist <- lapply(model.list.download, get_historical_nc, model.var = "tos") %>% 
  bind_rows

data.cimp6.table <- bind_rows(data.cimp6.hist, data.cimp6.sc)

write_csv(data.cimp6.table, "data_cimp6_table.csv")
                              
system("az vm deallocate --name atlantisserver01 --no-wait --resource-group morzariacedogroup")

```


Download salinity data for all scenarios
```{r}
model.list.download  <- c("GFDL-CM4", "CNRM-CM6-1-HR")
#model.list.download  <- c("CNRM-CM6-1-HR")

#sets working directory
setwd("~/Puget_Sound_Downscaling/data_files/")

#ScenarioMIP
#salinity is "sos"
data.cimp6.sc <- lapply(model.list.download, get_nc, model.var = "sos") %>% 
  bind_rows

#Historical data
#salinity is "sos"
data.cimp6.hist <- lapply(model.list.download, get_historical_nc, model.var = "sos") %>% 
  bind_rows

data.cimp6.table <- bind_rows(data.cimp6.hist, data.cimp6.sc)

write_csv(data.cimp6.table, "data_cimp6_table.csv")
                              
system("az vm deallocate --name atlantisserver01 --no-wait --resource-group morzariacedogroup")

```


Combine multipart files into a single nc file
```{r}

# list of all files with gr: "data reported on a model's regular grid"
model.files <- list.files("~/Puget_Sound_Downscaling/data_files", pattern = "*_gr_*.*nc$") 

# list of unique models and scenarios
model.scenarios <- list.files("~/Puget_Sound_Downscaling/data_files", pattern = "*_gr_*.*nc$") %>% 
  str_split(.,"_gr") %>% 
  unlist %>% 
  #switch between sos and tos. You can do this manually here, then rerun. ( Note on 7/20/20)
  grep("sos_Omon",., value = TRUE) %>% 
  unique()

data.path <- "~/Puget_Sound_Downscaling/data_files"
save.path <- "~/Puget_Sound_Downscaling/combined_data_files"
dir.create(save.path)

lapply(model.scenarios,combine_files, model.files, save.path, data.path)


```

Regrid files into common, highest resolution grid, in this case we are using GFDL-OM4p25 as the base grid
```{r}


# model resolution
# checked by opening nc file and printing open file 
# open netCDF file
# ncin <- nc_open(this.nc)
# print(this.file) #lists basic info about file
# GFDL-CM4 is ocean: GFDL-OM4p25 (GFDL-MOM6, tripolar - nominal 0.25 deg; 1440 x 1080 longitude/latitude; 75 levels; top grid cell 0-2 m)
# CNRM-CM6-1-HR, ocean: Nemo 3.6 (eORCA025, tripolar primarily 1/4deg; 1442 x 1050 longitude/latitude

data.path <- "~/Puget_Sound_Downscaling/combined_data_files"
save.path <- "~/Puget_Sound_Downscaling/regridded_data_files"
wgts.dir <- "~/Puget_Sound_Downscaling/wgts_files"
#will create directory if it does not exist
dir.create(save.path)
dir.create(wgts.dir)

# list of all files with gn: "data reported on a model's native grid"
model.files <- list.files(path=data.path, pattern = "*.*nc$") 
#switch variable here: sos or tos

mclapply(model.files, regrid_nc, save.path, data.path, wgts.dir, resolution = "1440x1080")


```


Calculate the climatology, the long term average for all nc files
- GFDL files were moved from combined_data_files to regridded_data_files
```{r}

data.path <- "~/Puget_Sound_Downscaling/regridded_data_files"
save.path <- "~/Puget_Sound_Downscaling/climatology_files"
#will create directory if it does not exist
dir.create(save.path)

# list of all regridded files
model.files <- list.files(path=data.path, pattern = "*.*nc$") 

# Calculate the number of cores
NumberOfCluster <- detectCores() - 1

# Initiate cluster
cl <- makeCluster(NumberOfCluster)
registerDoSNOW(cl)


point.data <- foreach(this.file = model.files, .verbose=TRUE) %dopar% {
  
  .packages = c(
    "tidyverse","ncdf4")
  
  if(length(.packages[!.inst]) > 0) install.packages(.packages[!.inst])
  
  # Load packages into session 
  lapply(.packages, require, character.only=TRUE)
  
  stat.clim <- "mean"
  
  climatology_nc(this.file, stat.clim, data.path, save.path)
  
}


```


Calculate anomaly as the difference between the hindcast and the forecast
```{r}

data.path <- "~/Puget_Sound_Downscaling/climatology_files"
save.path <- "~/Puget_Sound_Downscaling/anomaly_files"
#will create directory if it does not exist
dir.create(save.path)

# list of unique climatology files
models.cimp6 <- list.files(data.path, pattern = "ssp*.*_mean_*.*nc$") 
historical.files <- list.files(data.path, pattern = "historical*.*_mean_*.*nc$")

model.list <- c("CNRM-CM6-1-HR", "GFDL-CM4")

model.vars <- c("tos","sos")


lapply(model.list, anomaly_nc, models.cimp6, historical.files, model.vars)

```


Get SST from  NOAA OI SST V2 High Resolution Dataset: NOAA 1/4° daily Optimum Interpolation Sea Surface Temperature (or daily OISST) is an analysis constructed by combining observations from different platforms (satellites, ships, buoys, and Argo floats) on a regular global grid.
Reference is Reynolds, Richard W., Thomas M. Smith, Chunying Liu, Dudley B. Chelton, Kenneth S. Casey, Michael G. Schlax, 2007: Daily High-Resolution-Blended Analyses for Sea Surface Temperature. J. Climate, 20, 5473-5496. Cite as "NOAA High Resolution SST data provided by the NOAA/OAR/ESRL PSL, Boulder, Colorado, USA, from their Web site at https://psl.noaa.gov/"

```{r}
system("wget ftp://ftp.cdc.noaa.gov/Datasets/noaa.oisst.v2.highres/sst.day.mean.ltm.1982-2010.nc", wait=TRUE)

```

Get SST and salinity from NOAA 2018 World Ocean Atlas Dataset, 1° grid

```{r}
system("wget https://data.nodc.noaa.gov/thredds/fileServer/ncei/woa/temperature/decav/0.25/woa18_decav_t00_04.nc", wait =TRUE)

system("wget https://data.nodc.noaa.gov/thredds/fileServer/ncei/woa/salinity/decav/0.25/woa18_decav_s00_04.nc", wait=TRUE)
```


Get SST from RDA dataset ds548.0 - 'International Comprehensive Ocean-Atmosphere Data Set (ICOADS) Release 3, Individual Observations

```{r}

system("wget https://rda.ucar.edu/dsrqst/WALKER439286/ICOADS_R3.0_Rqst439286_19700101-19950422.csv.gz", wait=TRUE)
```



Interpolate values at 3km

```{r}

#GSHHS_f_L1 is layer imported from GIS with land shape. 

landShape <- readOGR("~/Puget_Sound_Downscaling/landshape_shapefile/", "GSHHS_f_L1")

# crop it to just puget sound, same as raster projection 
extent.study <- extent(-130, -121.5, 46, 51.5)
PugetSoundLandShape <- crop(landShape,extent.study)
#creating empty raster with 3km cell resolution
pred.raster <- raster(res=0.03)
#constrain raster to Puget Sound area
pred.raster.ext <- setExtent(pred.raster,extent.study,keepres = TRUE)
#convert polygon to raster using empty raster
PugetSoundRaster  <- rasterize(PugetSoundLandShape,pred.raster.ext,'level')
PugetSoundRaster <- setExtent(PugetSoundRaster, extent.study,keepres = TRUE)
plot(PugetSoundRaster)

#switch land values to NA, ocean to 1
PugetSoundRaster[is.na(PugetSoundRaster)] <- 2
PugetSoundRaster[PugetSoundRaster==1] <- NA
PugetSoundRaster[PugetSoundRaster==2] <- 1

data.path <- "~/Puget_Sound_Downscaling/anomaly_files"
save.path <- "~/Puget_Sound_Downscaling/3km_interpolated_files"
dir.create(save.path)

file.list <- list.files(data.path, pattern = "*.*nc$")
lapply(file.list, InterpolateData,PugetSoundRaster,data.path,save.path)

```

Plot Interpolated SST Anomalies for Salish Sea
```{r}
data.path<- "~/Puget_Sound_Downscaling/3km_interpolated_files/"
save.path<- "~/Puget_Sound_Downscaling/interpolated_anomaly_plots/"
#will create directory if it does not exist
dir.create(save.path)

file.list <- list.files(data.path, pattern = "tos*.*.*asc$")

lapply(file.list, plot_SSTanomaly,data.path,save.path)


```

Plot Interpolated Salinity Anomalies for Salish Sea
```{r}
data.path<- "~/Puget_Sound_Downscaling/3km_interpolated_files/"
save.path<- "~/Puget_Sound_Downscaling/interpolated_anomaly_plots/"
#will create directory if it does not exist
dir.create(save.path)

file.list <- list.files(data.path, pattern = "sos*.*.*asc$")

lapply(file.list, plot_salinity_anomaly,data.path,save.path)

```

Plot Faceted Interpolated Anomaly Figure
```{r}
setwd("~/Puget_Sound_Downscaling/interpolated_anomaly_plots/")
plot1 <- readPNG('sos_Omon_GFDL-CM4_ssp585_r1i1p1f1_anomaly_202001-205012_plot.png')
plot2 <- readPNG('sos_Omon_GFDL-CM4_ssp585_r1i1p1f1_anomaly_207001-210012_plot.png')
plot3 <- readPNG('tos_Omon_GFDL-CM4_ssp585_r1i1p1f1_anomaly_202001-205012_plot.png')
plot4 <- readPNG('tos_Omon_GFDL-CM4_ssp585_r1i1p1f1_anomaly_207001-210012_plot.png')

grid.combine <- grid.arrange(rasterGrob(plot1),rasterGrob(plot2),rasterGrob(plot3),rasterGrob(plot4),ncol=2)

ggsave(grid.combine, filename = "Fig3_Salish_Sea_Interpolated_Anomalies.png", device = "png", path = "~/Puget_Sound_Downscaling/final_figures/", 
       dpi = 100, width = 24, height = 20, units = "cm")

```


Interpolate 0.01 km anomalies

```{r}


#GSHHS_f_L1 is layer imported from GIS with land shape. 

landShape <- readOGR("~/Puget_Sound_Downscaling/landshape_shapefile/", "GSHHS_f_L1")

# crop it to just puget sound, same as raster projection 
extent.study <- extent(-130, -121.5, 46, 51.5)
PugetSoundLandShape <- crop(landShape,extent.study)
ps.crs <- crs(PugetSoundLandShape)

#creating empty raster with 3km cell resolution
pred.raster <- raster(extent.study, res=0.001)
PugetSoundRaster  <- rasterize(PugetSoundLandShape,pred.raster,'level')
plot(PugetSoundRaster)

#switch land values to NA, ocean to 1
PugetSoundRaster[is.na(PugetSoundRaster)] <- 2
PugetSoundRaster[PugetSoundRaster==1] <- NA
PugetSoundRaster[PugetSoundRaster==2] <- 1

data.path <- "~/Puget_Sound_Downscaling/anomaly_files"
save.path <- "~/Puget_Sound_Downscaling/interpolated_files"
dir.create(save.path)

file.list <- list.files(data.path, pattern = "*.*nc$")

#always check computer size
NumberOfCluster <- detectCores() - 4

# Initiate cluster
cl <- makeCluster(NumberOfCluster)
registerDoSNOW(cl)


interpolated.data <- foreach(this.file = file.list, .verbose=TRUE) %dopar% {
  
  .packages = c("fields","ncdf4","sf","rgdal","raster","stringr")
  
  if(length(.packages[!.inst]) > 0) install.packages(.packages[!.inst])
  
  # Load packages into session 
  lapply(.packages, require, character.only=TRUE)
  
  InterpolateData(this.file, PugetSoundRaster,data.path,save.path)
  
}


```


Take original ROMS time series and overlay anomalies

```{r}

setwd("~/Puget_Sound_Downscaling/Atlantis_shapefile/")
PugetSoundAtlantisPolygons  <- readOGR(".","bgm_Puget_Sound_89b_0p0001_WGS84")
#plot(PugetSoundAtlantisPolygons, add=TRUE)

#temperature ROMS time series used to drive Atlantis
# 2yr timeseries for 2005 and 2006, timestep is 12 hours 

atlantis.temp.roms <- "pugetsound_roms_temp.nc"

atlantis.salt.roms <- "pugetsound_roms_salt.nc"

#dim(temperatureArray)
#[1]    7   89 1460
# Note this is layers 1-7,  listed as deepest to shallowest, then blanks, then sediemntn. See user manual. 

#---------------
# Need to get the number of depth layers for each of the 89 Atlantis polygons, and a count of total num polygons
AtlantisBoxInfo <- read.csv(paste0("~/Puget_Sound_Downscaling/roms_forcing/","AtlantisBoxInfo.csv"))
#AtlantisBoxInfo$num_layers
#AtlantisBoxInfo$box_id

data.path <- "~/Puget_Sound_Downscaling/interpolated_files"
forcing.path <- "~/Puget_Sound_Downscaling/roms_forcing"

save.path <- "~/Puget_Sound_Downscaling/overlay_files"
dir.create(save.path)

file.list <- list.files(data.path, pattern = "*.*asc$")

 lapply(file.list,overlay_roms, PugetSoundAtlantisPolygons, AtlantisBoxInfo,atlantis.temp.roms, atlantis.salt.roms, data.path, save.path)
  


```

Combining the ROMS time series to prepare for plotting
```{r}

data.path <- "~/Puget_Sound_Downscaling/overlay_files"
save.path <- "~/Puget_Sound_Downscaling/"
setwd(data.path)

files.overlay <- list.files(data.path, pattern = "*.csv", full.names = TRUE) 

get_file <- function(this.file) {
  
  file_data<- fread(this.file) %>%
    as_tibble() %>%
    mutate(file_name= gsub("/home/atlantis/Puget_Sound_Downscaling/overlay_files/", "", this.file)) %>%
    mutate(boxIndex= boxIndex-1)# %>%
    #mutate(day = timestep/2) %>%
    #mutate(month = seq(as.Date("2005/1/1"), by = "day", length.out = 87600))

  return(file_data)
  
}

data.downscaled <- lapply(files.overlay, get_file) %>%
  bind_rows()

data.downscaled.table <- data.downscaled %>% 
    separate(file_name,
             into=c("variable",
                    "realm",
                    "model",
                    "experiment",
                    "realisation",
                    "stat",
                    "date"),
             sep = "_")
setwd("~/Puget_Sound_Downscaling/")
write_csv(data.downscaled.table, "data_downscaled_table.csv")


```

Grouping downscaled data to prepare for plotting 
```{r}

data.downscaled.table<- read_csv("data_downscaled_table.csv")

#including box
box.SST.grouping <- data.downscaled.table %>%
  group_by(variable, model, experiment, boxIndex, date) %>%
  filter(variable=="tos") %>%
  summarize(mean.roms_original = mean(roms_original), 
            mean.roms_cimp6 = mean(roms_cimp6)) %>%
  ungroup() %>%
  mutate(term=if_else(date =="202001-205012roms.csv", "Short-term",
                      if_else(date =="207001-210012roms.csv", "Long-term", "NA")))

setwd("~/Puget_Sound_Downscaling/Atlantis_shapefile/")
PugetSoundAtlantisPolygons  <-readOGR(".","bgm_Puget_Sound_89b_0p0001_WGS84")
#plot(PugetSoundAtlantisPolygons, add=TRUE)
library(broom)
spdf_fortified <- tidy(PugetSoundAtlantisPolygons, region = "code")

```

Plotting final figures
```{r}

setwd("~/Puget_Sound_Downscaling/")

#Figure 4 - plots SST 4 panel figure showing average temporal change for each scenario, model, and term
source("plot_SST_scenarios.R")

#Figure 5 - plots salinity 4 panel figure showing average temporal change for each scenario, model, and term
source("plot_salinity_scenarios.R")

#plots a scenario example of variability between models
source("plot_model_variability.R")

#plots an example of regional salinity differences in both terms
source("plot_salinity_chloropleth.R")

#faceting chloropleth figures
grid.combine <- grid.arrange(SSTmodel.map2, SSTmodel.map1, SALmodel.map2, SALmodel.map1, ncol =2, nrow=2)
ggsave(grid.combine, filename = "Fig7_combined_choropleth.png", device = "png", path = save.path, 
       dpi = 100, width = 24, height = 20, units = "cm")
```
Plotting choropleth figures
```{r}

#creates SST choropleth figures
source('~/Puget_Sound_Downscaling/make_SST_choropleth.R')

#creates salinity choropleth figures
source('~/Puget_Sound_Downscaling/make_salinity_chloropleth.R')

#set directory and load data.downscaled.table
setwd("~/Puget_Sound_Downscaling/")
data.downscaled.table <- fread("data_downscaled_table.csv")

#GFDL ssp585 SST (labeled differently because these are for Figure 7)
make_SST_chloropleth(data.downscaled.table, model.type = "GFDL-CM4", experiment.type ="ssp585", 
                 plot.filename1="SST_long.term_choropleth.png", plot.filename2 = "SST_short-term_choropleth.png",
                 combined.filename="SST_combined_choropleth.png", save.path = "~/Puget_Sound_Downscaling/final_figures/")

#GFDL ssp585 salinity (labeled differently because these are for Figure 7)
make_salinity_chloropleth(data.downscaled.table, model.type = "GFDL-CM4", experiment.type ="ssp585", plot.filename1="salinity_long.term_choropleth.png", plot.filename2 = "salinity_short-term_choropleth.png", combined.filename="salinity_combined_choropleth.png", save.path = "~/Puget_Sound_Downscaling/final_figures/")

#GFDL ssp245 SST
model.type= "GFDL-CM4"
experiment.type = "ssp245"
make_SST_chloropleth(data.downscaled.table, model.type = "GFDL-CM4", experiment.type ="ssp245", 
                 plot.filename1= paste0("SST_long-term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 = paste0("SST_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                 combined.filename= paste0("SST_combined_choropleth_",model.type,"_",experiment.type,".png" ), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#GFDL ssp245 salinity
model.type= "GFDL-CM4"
experiment.type = "ssp245"
make_salinity_chloropleth(data.downscaled.table, model.type = "GFDL-CM4", experiment.type ="ssp245", 
                     plot.filename1=paste0("salinity_long-term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 = paste0("salinity_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                     combined.filename=paste0("salinity_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#CNRM ssp126 SST
model.type = "CNRM-CM6-1-HR"
experiment.type = "ssp126"
make_SST_chloropleth(data.downscaled.table, model.type = "CNRM-CM6-1-HR", experiment.type ="ssp126", 
                 plot.filename1=paste0("SST_long-term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 =paste0("SST_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                combined.filename=paste0("SST_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#CNRM ssp126 salinity
model.type = "CNRM-CM6-1-HR"
experiment.type = "ssp126"
make_salinity_chloropleth(data.downscaled.table, model.type = "CNRM-CM6-1-HR", experiment.type ="ssp126", 
                 plot.filename1=paste0("salinity_long-term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 =paste0("salinity_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                combined.filename=paste0("salinity_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#CNRM ssp245 SST
model.type = "CNRM-CM6-1-HR"
experiment.type = "ssp245"
make_SST_chloropleth(data.downscaled.table, model.type = "CNRM-CM6-1-HR", experiment.type ="ssp245", 
                 plot.filename1=paste0("SST_long-term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 =paste0("SST_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                combined.filename=paste0("SST_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#CNRM ssp245 salinity
model.type = "CNRM-CM6-1-HR"
experiment.type = "ssp245"
make_salinity_chloropleth(data.downscaled.table, model.type = "CNRM-CM6-1-HR", experiment.type ="ssp245", 
                 plot.filename1=paste0("salinity_long.term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 =paste0("salinity_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                combined.filename=paste0("salinity_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#CNRM ssp370 SST
model.type = "CNRM-CM6-1-HR"
experiment.type = "ssp370"
make_SST_chloropleth(data.downscaled.table, model.type = "CNRM-CM6-1-HR", experiment.type ="ssp370", 
                 plot.filename1=paste0("SST_long.term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 =paste0("SST_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                combined.filename=paste0("SST_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#CNRM ssp370 salinity
model.type = "CNRM-CM6-1-HR"
experiment.type = "ssp370"
make_salinity_chloropleth(data.downscaled.table, model.type = "CNRM-CM6-1-HR", experiment.type ="ssp370", 
                 plot.filename1=paste0("salinity_long.term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 =paste0("salinity_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                combined.filename=paste0("salinity_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#CNRM ssp585 SST
model.type = "CNRM-CM6-1-HR"
experiment.type = "ssp585"
make_SST_chloropleth(data.downscaled.table, model.type = "CNRM-CM6-1-HR", experiment.type ="ssp585", 
                 plot.filename1=paste0("SST_long.term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 =paste0("SST_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                combined.filename=paste0("SST_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")

#CNRM ssp585 salinity
model.type = "CNRM-CM6-1-HR"
experiment.type = "ssp585"
make_salinity_chloropleth(data.downscaled.table, model.type = "CNRM-CM6-1-HR", experiment.type ="ssp585", 
                 plot.filename1=paste0("salinity_long.term_choropleth_",model.type,"_",experiment.type,".png"), plot.filename2 =paste0("salinity_short-term_choropleth_",model.type,"_",experiment.type,".png"),
                combined.filename=paste0("salinity_combined_choropleth_",model.type,"_",experiment.type,".png"), save.path = "~/Puget_Sound_Downscaling/final_figures/")
```
Faceting choropleth figures (Fig 7)
```{r}
setwd("~/Puget_Sound_Downscaling/final_figures/")
save.path <- "~/Puget_Sound_Downscaling/final_figures/"

#combining GFDL ssp585
SST_combined <-readPNG('SST_combined_choropleth.png')
salinity_combined <- readPNG('salinity_combined_choropleth.png')

grid.combine <- grid.arrange(rasterGrob(SST_combined),rasterGrob(salinity_combined),nrow=2)

ggsave(grid.combine, filename = "Fig7_combined_choropleth.png", device = "png", path = save.path, 
       dpi = 100, width = 24, height = 20, units = "cm")

#combining GFDL ssp245
SST_combined <-readPNG('SST_combined_choropleth_GFDL-CM4_ssp245.png')
salinity_combined <- readPNG('salinity_combined_choropleth_GFDL-CM4_ssp245.png')

grid.combine <- grid.arrange(rasterGrob(SST_combined),rasterGrob(salinity_combined),nrow=2)

ggsave(grid.combine, filename = "GFDL_ssp245_SST_salinity_combined_choropleth.png", device = "png", path = save.path, 
       dpi = 100, width = 24, height = 20, units = "cm")

#combining CNRM ssp126
SST_combined <-readPNG('SST_combined_choropleth_CNRM-CM6-1-HR_ssp126.png')
salinity_combined <- readPNG('salinity_combined_choropleth_CNRM-CM6-1-HR_ssp126.png')

grid.combine <- grid.arrange(rasterGrob(SST_combined),rasterGrob(salinity_combined),nrow=2)

ggsave(grid.combine, filename = "CNRM-CM6-1-HR_ssp126_SST_salinity_combined_choropleth.png", device = "png", path = save.path, 
       dpi = 100, width = 24, height = 20, units = "cm")

#combining CNRM ssp245
SST_combined <-readPNG('SST_combined_choropleth_CNRM-CM6-1-HR_ssp245.png')
salinity_combined <- readPNG('salinity_combined_choropleth_CNRM-CM6-1-HR_ssp245.png')

grid.combine <- grid.arrange(rasterGrob(SST_combined),rasterGrob(salinity_combined),nrow=2)

ggsave(grid.combine, filename = "CNRM-CM6-1-HR_ssp245_SST_salinity_combined_choropleth.png", device = "png", path = save.path, 
       dpi = 100, width = 24, height = 20, units = "cm")

#combing CNRM ssp370
SST_combined <-readPNG('SST_combined_choropleth_CNRM-CM6-1-HR_ssp370.png')
salinity_combined <- readPNG('salinity_combined_choropleth_CNRM-CM6-1-HR_ssp370.png')

grid.combine <- grid.arrange(rasterGrob(SST_combined),rasterGrob(salinity_combined),nrow=2)

ggsave(grid.combine, filename = "CNRM-CM6-1-HR_ssp370_SST_salinity_combined_choropleth.png", device = "png", path = save.path, 
       dpi = 100, width = 24, height = 20, units = "cm")

#combining CNRM ssp585
SST_combined <-readPNG('SST_combined_choropleth_CNRM-CM6-1-HR_ssp585.png')
salinity_combined <- readPNG('salinity_combined_choropleth_CNRM-CM6-1-HR_ssp585.png')

grid.combine <- grid.arrange(rasterGrob(SST_combined),rasterGrob(salinity_combined),nrow=2)

ggsave(grid.combine, filename = "CNRM-CM6-1-HR_ssp585_SST_salinity_combined_choropleth.png", device = "png", path = save.path, 
       dpi = 100, width = 24, height = 20, units = "cm")
```

Faceting SST interpolated anomaly figures for supplementary material
```{r}
setwd("~/Puget_Sound_Downscaling/interpolated_anomaly_plots/")
save.path <- "~/Puget_Sound_Downscaling/final_figures/faceted_interpolated_anomalies/"

#combining GFDL ssp585 SST
long.term <-readPNG('tos_Omon_GFDL-CM4_ssp585_r1i1p1f1_anomaly_207001-210012_plot.png')
short.term <- readPNG('tos_Omon_GFDL-CM4_ssp585_r1i1p1f1_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "SST_interpolated_anomaly_combined_GFDL-CM4_ssp585.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining GFDL ssp245 SST
long.term <-readPNG('tos_Omon_GFDL-CM4_ssp245_r1i1p1f1_anomaly_207001-210012_plot.png')
short.term <- readPNG('tos_Omon_GFDL-CM4_ssp245_r1i1p1f1_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "SST_interpolated_anomaly_combined_GFDL-CM4_ssp245.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining CNRM ssp585 SST
long.term <-readPNG('tos_Omon_CNRM-CM6-1-HR_ssp585_r1i1p1f2_anomaly_207001-210012_plot.png')
short.term <- readPNG('tos_Omon_CNRM-CM6-1-HR_ssp585_r1i1p1f2_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "SST_interpolated_anomaly_combined_CNRM-CM6-1-HR_ssp585.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining CNRM ssp370 SST
long.term <-readPNG('tos_Omon_CNRM-CM6-1-HR_ssp370_r1i1p1f2_anomaly_207001-210012_plot.png')
short.term <- readPNG('tos_Omon_CNRM-CM6-1-HR_ssp370_r1i1p1f2_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "SST_interpolated_anomaly_combined_CNRM-CM6-1-HR_ssp370.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining CNRM ssp245 SST
long.term <-readPNG('tos_Omon_CNRM-CM6-1-HR_ssp245_r1i1p1f2_anomaly_207001-210012_plot.png')
short.term <- readPNG('tos_Omon_CNRM-CM6-1-HR_ssp245_r1i1p1f2_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "SST_interpolated_anomaly_combined_CNRM-CM6-1-HR_ssp245.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining CNRM ssp126 SST
long.term <-readPNG('tos_Omon_CNRM-CM6-1-HR_ssp126_r1i1p1f2_anomaly_207001-210012_plot.png')
short.term <- readPNG('tos_Omon_CNRM-CM6-1-HR_ssp126_r1i1p1f2_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "SST_interpolated_anomaly_combined_CNRM-CM6-1-HR_ssp126.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

```

Faceting salinity interpolated anomaly figures for supplementary material
```{r}
setwd("~/Puget_Sound_Downscaling/interpolated_anomaly_plots/")
save.path <- "~/Puget_Sound_Downscaling/final_figures/faceted_interpolated_anomalies/"

#combining GFDL ssp585 salinity
long.term <-readPNG('sos_Omon_GFDL-CM4_ssp585_r1i1p1f1_anomaly_207001-210012_plot.png')
short.term <- readPNG('sos_Omon_GFDL-CM4_ssp585_r1i1p1f1_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "salinity_interpolated_anomaly_combined_GFDL-CM4_ssp585.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining GFDL ssp245 salinity
long.term <-readPNG('sos_Omon_GFDL-CM4_ssp245_r1i1p1f1_anomaly_207001-210012_plot.png')
short.term <- readPNG('sos_Omon_GFDL-CM4_ssp245_r1i1p1f1_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "salinity_interpolated_anomaly_combined_GFDL-CM4_ssp245.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining CNRM ssp585 salinity
long.term <-readPNG('sos_Omon_CNRM-CM6-1-HR_ssp585_r1i1p1f2_anomaly_207001-210012_plot.png')
short.term <- readPNG('sos_Omon_CNRM-CM6-1-HR_ssp585_r1i1p1f2_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "salinity_interpolated_anomaly_combined_CNRM-CM6-1-HR_ssp585.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining CNRM ssp370 salinity
long.term <-readPNG('sos_Omon_CNRM-CM6-1-HR_ssp370_r1i1p1f2_anomaly_207001-210012_plot.png')
short.term <- readPNG('sos_Omon_CNRM-CM6-1-HR_ssp370_r1i1p1f2_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "salinity_interpolated_anomaly_combined_CNRM-CM6-1-HR_ssp370.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining CNRM ssp245 salinity
long.term <-readPNG('sos_Omon_CNRM-CM6-1-HR_ssp245_r1i1p1f2_anomaly_207001-210012_plot.png')
short.term <- readPNG('sos_Omon_CNRM-CM6-1-HR_ssp245_r1i1p1f2_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "salinity_interpolated_anomaly_combined_CNRM-CM6-1-HR_ssp245.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

#combining CNRM ssp126 salinity
long.term <-readPNG('sos_Omon_CNRM-CM6-1-HR_ssp126_r1i1p1f2_anomaly_207001-210012_plot.png')
short.term <- readPNG('sos_Omon_CNRM-CM6-1-HR_ssp126_r1i1p1f2_anomaly_202001-205012_plot.png')

grid.combine <- grid.arrange(rasterGrob(short.term),rasterGrob(long.term),ncol=2)

ggsave(grid.combine, filename = "salinity_interpolated_anomaly_combined_CNRM-CM6-1-HR_ssp126.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

```

Faceting resolution images for supplementary material
```{r}
setwd("~/Puget_Sound_Downscaling/resolution_images/")
save.path <- "~/Puget_Sound_Downscaling/final_figures/"

CNRM.res <- ReadPNG('CNRM-CM6-1-HR_resolution.png')
GFDL.res <- ReadPNG('GFDL-CM4_resolution.png')

grid.combine <- grid.arrange(rasterGrob(CNRM.res),rasterGrob(GFDL.res),ncol=2)

ggsave(grid.combine, filename = "original_GCM_grid_resolution_combined.png", device = "png", path = save.path, 
       dpi = 150, width = 13, height = 11, units = "cm")

```

